Tree-structured neural networks revisited

### 2016-03-02 writing/hard_stack_paper/paper.tex
Paper update.

\begin{figure}[t]
\begin{subfigure}[t]{0.9\columnwidth}
\vspace{14em}
\todo{[SB] Figure showing why trees can't be batched.}

@@

\begin{subfigure}[t]{0.9\columnwidth}
\vspace{14em}
\todo{[SB] Figure showing why trees can't be batched.}

@@

@@

@@

We used random search to tune \todo{[SB] List tuned hyperparameters.}

We trained each model for 250k steps, using a minibatch size of 64 for each step. We tracked each model's performance on the development set during training and saving parameters when this performance reached a new peak. We used early stopping, evaluating on the test set using the parameters that performed best on the development set.

@@

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Trained params.    &   Train  &   Test \\
\midrule
\multicolumn{4}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                 &   99.7   &   78.2      \\
\midrule
\multicolumn{4}{c}{Previous NN results without attention}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m               &   83.4   &   82.1       \\
\todo{[SB] Import baselines from page}  
                        & ?                  &   ?      &   81?       \\
\midrule
\multicolumn{4}{c}{Previous NN results with attention}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long} (1.4m params) 92.3    89.1

>>>>

\begin{figure}[t]
\begin{subfigure}[t]{0.9\columnwidth}
\vspace{14em}
\todo{[SB] Figure showing why trees can't be batched (modeled after slides).}

@@

\begin{subfigure}[t]{0.9\columnwidth}
\vspace{14em}
\todo{[SB] Figure showing a batch of sequences (modeled after slides).}

@@

\vspace{10em}

@@

\vspace{8em}

@@

We use the RMSProp optimizer (\todo{Cite.}) with a tuned starting learning rate that decays by a factor of 0.75 every 10k steps. We apply both dropout \cite{srivastava2014dropout} and batch normalization \cite{2015SIoffeCSzegedy} to the word embeddings in the buffer (after the linear projection is applied) and to the feature vectors that serve as the inputs and outputs to the MLP that precedes the final entailment classifier. In addition, we apply an L2 regularization penalty to all parameters.

We used random search to tune many of the hyperparameters, including the learning rate, the dropout rate, the L2 regularization weight, the hidden dimension of the tracking LSTM and the number of layers in the MLP \todo{[SB] Report the ranges searched for each parameter and the number of runs for each results.}

We trained each model for 250k steps in each run, using a minibatch size of 64 for each step. We tracked each model's performance on the development set during training and saving parameters when this performance reached a new peak. We used early stopping, evaluating on the test set using the parameters that performed best on the development set.

@@

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Trained params.    &   Train  &   Test \\
\midrule
\multicolumn{4}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                 &   99.7   &   78.2      \\
\midrule
\multicolumn{4}{c}{Previous NN results without attention}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m               &   83.4   &   82.1       \\
\midrule
\multicolumn{4}{c}{Previous NN results with attention}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long} (1.4m params) 92.3    89.1
